BlueTracer: \\ a Robust API Tracer for Evasive Malware

### 2018-07-19 Msc-Slides/main.tex
Final fixes

\section{Intro.}

@@

         \begin{beamerboxesrounded}[shadow=true]{}
    Dynamic analysis strongly favoured as it allows to dodge most code obfuscations and deal with a large number of samples
    \end{beamerboxesrounded}

@@

Available API tracing tools have \textbf{limited logging capabilities}
%\begin{itemize}
%\item[--] The amount of recorded information is too little
%\end{itemize}
\medskip
	\begin{block}{}
\begin{lstlisting}[basicstyle=\ttfamily\large,xleftmargin=50pt]
<@\textcolor{red}{record\_before(libcall\_name, arg1)}@> 
retval = libcall(arg1, &arg2)
<@\textcolor{red}{record\_after(retval, *arg2)}@> 
\end{lstlisting}
\end{block}	
\medskip
\begin{itemize}
\item Access to calls related information is required
\begin{itemize}
\item[--] Prototype (number of arguments, data types, input/output)
\item[--] Need to know their run-time locations
\end{itemize}
\medskip
\item \textbf{Challenge:} heterogeneity of Windows libraries used in malware and lack of well-structured documentation for their prototypes
\end{itemize}

@@

\textcolor{sapienza}{\textbf{The tool possesses a remarkable logging power:}}
\begin{itemize}
%\item Integration of reliable external sources \\ (\textbf{Dr. %Memory}
%and \textbf{CISCO PyREBox})
%\item Logging operations are challenging 
%by the heterogeneity of Windows libraries used in malware and the lack of well-structured documentation for their prototypes
%\begin{itemize}
\item Integration of rich, reliable external sources \\ (\textbf{Dr. Memory}
and \textbf{CISCO PyREBox})
%\end{itemize} 
%\end{itemize}

%\textcolor{sapienza}{\textbf{Key features:}}
%\begin{itemize}
\item Stealthy tracing of input parameters, output buffers and return values of over 17,000 system calls and library calls
\item Logging of asynchronous events
%\item Allows to trace only calls from the main executable
\end{itemize}

@@

    \begin{table}[h]
\vspace*{-0.1cm}
\begin{center}
\resizebox{9.2cm}{!}{
 \begin{tabular}{||c c c||}
 \hline
 \textbf{ID} & \textbf{MD5} & \textbf{Name} \\ 
 \hline\hline
 1 & 0af4ef5069f47a371a0caf22ae2006a6 & \textit{banker} \\ 
 \hline
 2 & 9437eabf2fe5d32101e3fbf9f6027880 & \textit{dropper} \\
 \hline
 3 & cbdda646a20d95f078393506ecdc0796 & \textit{trojan}\\
 \hline
 4 & cfdd16225e67471f5ef54cab9b3a5558 & Olympic\\
 \hline
 5 & ef694b89ad7addb9a16bb6f26f1efaf7 & Malicious CCleaner\\ 
 \hline
\end{tabular}
}
\end{center}
\end{table}
\vspace{-0.1cm}
Manual validation of all relevant actions performed by each sample:
\vspace{-0.5cm}
\begin{itemize}
\item Check if logs are congruous with Joe Security reports
\item Process Monitor as ground truth for system activity
\end{itemize}
\medskip
\begin{beamerboxesrounded}[shadow=true]{}
The
logs collected by BlueTracer reveal behaviors consistent with the analysis reports
authored by Joe Security
\end{beamerboxesrounded}

@@

\begin{lstlisting}
~~1116~~ 138 kernel32.dll!CopyFileA
138 	arg 0: <@\alert{C:\textbackslash Users\textbackslash Simuset\textbackslash Desktop\textbackslash sample1.exe}@> 
(name=lpExistingFileName, type=char*, size=0x1)
138 	arg 1: <@\alert{C:\textbackslash Windows\textbackslash system32\textbackslash $\dagger$\textbackslash ffpb6966.exe}@> 
(name=lpNewFileName, type=char*, size=0x1)
138 	arg 2: <@\alert{0x0}@> (name=bFailIfExists, type=(long/int), size=0x4)
138    executed kernel32.dll!CopyFileA =>
138 	retval:<@\alert{0x1}@> (name=Return value, type=(long/int), size=0x4)
\end{lstlisting}

>>>>

\section{Introduction}

@@

         \begin{beamerboxesrounded}[shadow=true]{}
    Dynamic analysis strongly favoured as it allows us to dodge most code obfuscations and deal with a large number of samples
    \end{beamerboxesrounded}

@@

Available API tracing tools have \textbf{limited logging capabilities}
%\begin{itemize}
%\item[--] The amount of recorded information is too little
%\end{itemize}
\medskip
	\begin{block}{}
\begin{lstlisting}[basicstyle=\ttfamily\large,xleftmargin=50pt]
<@\textcolor{red}{record\_before(libcall\_name, arg1)}@> 
retval = libcall(arg1, &arg2)
<@\textcolor{red}{record\_after(retval, *arg2)}@> 
\end{lstlisting}
\end{block}	
\medskip
\begin{itemize}
\item Access to function calls information is required
\begin{itemize}
\item[--] Prototype (number of arguments, data types, input/output)
\end{itemize}
\medskip
\item \textbf{Challenge:} heterogeneity of Windows libraries used in malware and lack of well-structured documentation for their prototypes
\end{itemize}

@@

\textcolor{sapienza}{\textbf{The tool possesses a remarkable logging power:}}
\begin{itemize}
%\item Integration of reliable external sources \\ (\textbf{Dr. %Memory}
%and \textbf{CISCO PyREBox})
%\item Logging operations are challenging 
%by the heterogeneity of Windows libraries used in malware and the lack of well-structured documentation for their prototypes
%\begin{itemize}
\item Integration of rich, reliable external sources of function prototypes information  \\ (\textbf{Dr. Memory}
and \textbf{CISCO PyREBox})
%\end{itemize} 
%\end{itemize}

%\textcolor{sapienza}{\textbf{Key features:}}
%\begin{itemize}
\item Stealthy tracing of input parameters, output buffers and return values of all system calls and of over 17,000 library calls
\item Logging of asynchronous events
%\item Allows to trace only calls from the main executable
\end{itemize}

@@

    \begin{table}[h]
\vspace*{-0.1cm}
\begin{center}
\resizebox{9.2cm}{!}{
 \begin{tabular}{||c c c||}
 \hline
 \textbf{ID} & \textbf{MD5} & \textbf{Name} \\ 
 \hline\hline
 1 & 0af4ef5069f47a371a0caf22ae2006a6 & \textit{banker} \\ 
 \hline
 2 & 9437eabf2fe5d32101e3fbf9f6027880 & \textit{dropper} \\
 \hline
 3 & cbdda646a20d95f078393506ecdc0796 & \textit{trojan}\\
 \hline
 4 & cfdd16225e67471f5ef54cab9b3a5558 & Olympic\\
 \hline
 5 & ef694b89ad7addb9a16bb6f26f1efaf7 & Malicious CCleaner\\ 
 \hline
\end{tabular}
}
\end{center}
\end{table}
\vspace{-0.1cm}
Manual validation of all relevant actions performed by each sample:
\vspace{-0.5cm}
\begin{itemize}
\item Check if logs are congruous with Joe Security reports
\end{itemize}
\medskip
\begin{beamerboxesrounded}[shadow=true]{}
The
logs collected by BlueTracer reveal behaviors consistent with the analysis reports
authored by Joe Security
\end{beamerboxesrounded}

@@

\begin{lstlisting}
[PID: 1116] kernel32.dll!CopyFileA
arg 0:  <@\alert{C:\textbackslash Users\textbackslash Simuset\textbackslash Desktop\textbackslash sample1.exe}@> 
        (name=lpExistingFileName, type=char*, size=0x1)
arg 1:  <@\alert{C:\textbackslash Windows\textbackslash system32\textbackslash $\dagger$\textbackslash ffpb6966.exe}@> 
        (name=lpNewFileName, type=char*, size=0x1)
arg 2:  <@\alert{0x0}@> 
        (name=bFailIfExists, type=(long/int), size=0x4)
retval: <@\alert{0x1}@> 
        (name=Return value, type=(long/int), size=0x4)
\end{lstlisting}
